Scheeper's Meager-NWD Game and the Menger Game

### 2014-07-30 phd/dissertation/chapter2.tex
no umlaut in markov

\begin{defn}
  For a game $G=\<M,W\>$, the \term{$k$-tactical fog-of-war} is the function
  $\nu_k:M^{<\omega}\to M^{\leq k}$ defined by
    \[
      \nu_k(\<m_0,\dots,m_{n-1}\>)=\<m_{n-k},\dots,m_{n-1}\>
    \]
  and the \term{$k$-Mark\"ov fog-of-war} is the function
  $\mu_k:M^{<\omega}\to (M^{\leq k}\times\omega)$ defined by
    \[
      \mu_k(\<m_0,\dots,m_{n-1}\>)=\<\<m_{n-k},\dots,m_{n-1}\>,n\>
    \]
\end{defn}

@@

  A \term{$k$-Mark\"ov strategy} or \term{$k$-mark} is a function
  $\sigma:M^{\leq k}\times\omega\to M$ yielding a corresponding strategy
  $\sigma\circ\mu_k:M^{<\omega}\to M$.
\end{defn}

@@

The $k$ is usually omitted when $k=1$. A ($1$-)tactic is
called a \term{stationary strategy} by some authors. $0$-tactics are not
usually interesting (such strategies would be constant functions); however,
we will discuss $0$-Mark\"ov strategies, called
\term{predetermined strategies} since such a strategy only uses the round
number and does not rely on knowing which moves the opponent will make.
Of course, a limited information strategy $\sigma$ is \term{winning} for a
player if its corresponding strategy $\sigma\circ\nu_k$ or $\sigma\circ\mu_k$
is winning for that player.

@@

  If a winning $k$-Mark\"ov strategy exists for a player $\pl A$ in the game
  $G$, then we write $\pl A \kmarkwin{k} G$. If $k=1$, then $\pl A \markwin G$,
  and if $k=0$, then $\pl A \prewin G$.
\end{defn}

>>>>

\begin{defn}
  For a game $G=\<M,W\>$, the \term{$k$-tactical fog-of-war} is the function
  $\nu_k:M^{<\omega}\to M^{\leq k}$ defined by
    \[
      \nu_k(\<m_0,\dots,m_{n-1}\>)=\<m_{n-k},\dots,m_{n-1}\>
    \]
  and the \term{$k$-Markov fog-of-war} is the function
  $\mu_k:M^{<\omega}\to (M^{\leq k}\times\omega)$ defined by
    \[
      \mu_k(\<m_0,\dots,m_{n-1}\>)=\<\<m_{n-k},\dots,m_{n-1}\>,n\>
    \]
\end{defn}

@@

  A \term{$k$-Markov strategy} or \term{$k$-mark} is a function
  $\sigma:M^{\leq k}\times\omega\to M$ yielding a corresponding strategy
  $\sigma\circ\mu_k:M^{<\omega}\to M$.
\end{defn}

@@

The $k$ is usually omitted when $k=1$. A ($1$-)tactic is
called a \term{stationary strategy} by some authors. $0$-tactics are not
usually interesting (such strategies would be constant functions); however,
we will discuss $0$-Markov strategies, called
\term{predetermined strategies} since such a strategy only uses the round
number and does not rely on knowing which moves the opponent will make.
Of course, a limited information strategy $\sigma$ is \term{winning} for a
player if its corresponding strategy $\sigma\circ\nu_k$ or $\sigma\circ\mu_k$
is winning for that player.

@@

  If a winning $k$-Markov strategy exists for a player $\pl A$ in the game
  $G$, then we write $\pl A \kmarkwin{k} G$. If $k=1$, then $\pl A \markwin G$,
  and if $k=0$, then $\pl A \prewin G$.
\end{defn}

### 2014-07-30 phd/dissertation/chapter3.tex
no umlaut in markov

  For the forward implication, let $\sigma$ be a winning predetermined
  (perfect information) strategy, and $\lambda$ be the $0$-Mark\"ov
  fog-of-war $\mu_0$ (the identity).

@@

  In the final case, note that any Mark\"ov strategy $\sigma'$ for $\pl O$ may
  be strengthened to $\sigma$ defined by
  $\sigma(x,n)=\bigcap_{m\leq n}\sigma'(x,m)$.
  So, suppose that $\sigma$ is a winning Mark\"ov strategy for $\pl O$ in
  $\clusgame{X}{S}$ such that $\sigma(x,m)\supseteq\sigma(x,n)$ for all
  $m\leq n$.

  Let $p$ be a legal attack against $\sigma$, and $q$ be a subsequence of $p$.
  For $m<\omega$, there exists $f(m)\geq m$ such that $q(m)=p(f(m))$. It follows
  that
    $
      q(0)=p(f(0))
        \in
      \sigma(\emptyset,0)\cap \bigcap_{m\leq f(0)}\sigma(\<p(m)\>,m)
        \subseteq
      \sigma(\emptyset,0)
    $
  and
    \[
      \begin{array}{rcl}
        q(n+1)=p(f(n+1)) &
          \in &
        \displaystyle
        \sigma(\emptyset,0)\cap \bigcap_{m<f(n+1)}\sigma(\<p(m)\>,m+1) \\ &
          \subseteq &
        \displaystyle
        \sigma(\emptyset,0)\cap \bigcap_{m<n+1}\sigma(\<p(f(m))\>,f(m)+1) \\ &
          = &
        \displaystyle
        \sigma(\emptyset,0)\cap \bigcap_{m<n+1}\sigma(\<q(m)\>,f(m)+1) \\ &
          \subseteq &
        \displaystyle
        \sigma(\emptyset,0)\cap \bigcap_{m<n+1}\sigma(\<q(m)\>,m+1)
      \end{array}
    \]
  so $q$ is also a legal attack against $\sigma$. Since $\sigma$ is a winning
  strategy, $q$ clusters at $S$, and since every subsequence of $p$ clusters
  at $S$, $p$ must converge to $S$. Thus $\sigma$ is also a winning Mark\"ov
  strategy for $\pl O$ in $\congame{X}{S}$ as well.
\end{proof}

@@

This actually can be generalized to any $k$-Mark\"ov strategy with just
a little more bookkeeping.

@@

However, while the clustering and convergence variants are equivalent
for Mark\"ov strategies in the ``normal'' version of the $W$ game, they are
\textit{not} equivalent in the ``hard'' version.

@@

  We define the Mark\"ov strategy $\sigma$ by setting
    \[
      \sigma(\emptyset,0) = \sigma(\<\infty\>,n) = \oneptcomp\omega_1
    \]
  and for all $\alpha<\omega_1$ setting
    \[
      \sigma(\<\alpha\>,n) = \oneptcomp\omega_1 \setminus A_\alpha(n)
    \]

@@

\begin{proof}
  Let $\sigma$ be a $k$-mark for $\pl O$ in
  $\clusgame{\oneptcomp\omega_2}{\infty}$. By the closing-up lemma, the set
    \[
      C_\sigma
        =
      \{
        \alpha<\omega_2
          :
        s\in\alpha^{<\omega}
          \Rightarrow
        \oneptcomp\omega_2\setminus\sigma\circ\mu_k(s)
        \subset \alpha
      \}
    \]
  is closed and unbounded. (Recall that $\mu_k$ is the
  $k$-Mark\"ov fog-of-war which turns perfect information into the last $k$
  moves and the round number.) Let $a_\sigma:\omega_2\to C_\sigma$ be
  an order isomorphism.

>>>>

  For the forward implication, let $\sigma$ be a winning predetermined
  (perfect information) strategy, and $\lambda$ be the $0$-Markov
  fog-of-war $\mu_0$ (the identity).

@@

  In the final case, note that any Markov strategy $\sigma'$ for $\pl O$ may
  be strengthened to $\sigma$ defined by
  $\sigma(x,n)=\bigcap_{m\leq n}\sigma'(x,m)$.
  So, suppose that $\sigma$ is a winning Markov strategy for $\pl O$ in
  $\clusgame{X}{S}$ such that $\sigma(x,m)\supseteq\sigma(x,n)$ for all
  $m\leq n$.

  Let $p$ be a legal attack against $\sigma$, and $q$ be a subsequence of $p$.
  For $m<\omega$, there exists $f(m)\geq m$ such that $q(m)=p(f(m))$. It follows
  that
    $
      q(0)=p(f(0))
        \in
      \sigma(\emptyset,0)\cap \bigcap_{m\leq f(0)}\sigma(\<p(m)\>,m)
        \subseteq
      \sigma(\emptyset,0)
    $
  and
    \[
      \begin{array}{rcl}
        q(n+1)=p(f(n+1)) &
          \in &
        \displaystyle
        \sigma(\emptyset,0)\cap \bigcap_{m<f(n+1)}\sigma(\<p(m)\>,m+1) \\ &
          \subseteq &
        \displaystyle
        \sigma(\emptyset,0)\cap \bigcap_{m<n+1}\sigma(\<p(f(m))\>,f(m)+1) \\ &
          = &
        \displaystyle
        \sigma(\emptyset,0)\cap \bigcap_{m<n+1}\sigma(\<q(m)\>,f(m)+1) \\ &
          \subseteq &
        \displaystyle
        \sigma(\emptyset,0)\cap \bigcap_{m<n+1}\sigma(\<q(m)\>,m+1)
      \end{array}
    \]
  so $q$ is also a legal attack against $\sigma$. Since $\sigma$ is a winning
  strategy, $q$ clusters at $S$, and since every subsequence of $p$ clusters
  at $S$, $p$ must converge to $S$. Thus $\sigma$ is also a winning Markov
  strategy for $\pl O$ in $\congame{X}{S}$ as well.
\end{proof}

@@

This actually can be generalized to any $k$-Markov strategy with just
a little more bookkeeping.

@@

However, while the clustering and convergence variants are equivalent
for Markov strategies in the ``normal'' version of the $W$ game, they are
\textit{not} equivalent in the ``hard'' version.

@@

  We define the Markov strategy $\sigma$ by setting
    \[
      \sigma(\emptyset,0) = \sigma(\<\infty\>,n) = \oneptcomp\omega_1
    \]
  and for all $\alpha<\omega_1$ setting
    \[
      \sigma(\<\alpha\>,n) = \oneptcomp\omega_1 \setminus A_\alpha(n)
    \]

@@

\begin{proof}
  Let $\sigma$ be a $k$-mark for $\pl O$ in
  $\clusgame{\oneptcomp\omega_2}{\infty}$. By the closing-up lemma, the set
    \[
      C_\sigma
        =
      \{
        \alpha<\omega_2
          :
        s\in\alpha^{<\omega}
          \Rightarrow
        \oneptcomp\omega_2\setminus\sigma\circ\mu_k(s)
        \subset \alpha
      \}
    \]
  is closed and unbounded. (Recall that $\mu_k$ is the
  $k$-Markov fog-of-war which turns perfect information into the last $k$
  moves and the round number.) Let $a_\sigma:\omega_2\to C_\sigma$ be
  an order isomorphism.
